Meta-analysis of the Interoceptive Accuracy Scale

### 2025-10-31 analysis/Study1.qmd
updated script
minor

df17 <- haven::read_sav("../data/Petzke2024/ETUDE1_main study.sav") |>
  mutate_all(as.numeric) |>
  select(id, age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total) |>
  rename(Age= age_to_be_completed_that_year,
         Heart = IA01_01, Hungry = IA01_02, Breathing = IA01_03, Thirsty = IA01_04, Urinate = IA01_05, 
         Defecate=IA01_06, Taste = IA01_07,Vomit = IA01_08, Sneeze = IA01_09, Cough = IA01_10, 
         Temp = IA01_11, Sex_arousal = IA01_12, Wind = IA01_13, Burp = IA01_14,Muscles = IA01_15, 
         Bruise = IA01_16, Pain = IA01_17, Blood_Sugar = IA01_18, Affective_touch = IA01_19, 
         Tickle =IA01_20, Itch = IA01_21,
         TAS_DIF = DIF_total, TAS_DDF =  DDF_total, TAS_EOT = EOT_total,
         PHQ15_Sum = PHQ_15_total,
         PHQ4_Sum = PHQ_4_total,
         BPQ_BodyAwareness = BPQ_total,
          ) |>
  mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender == 3 ~ "Other"))|>
   mutate(
    Age_code = zap_labels(Age),      # remove SPSS labels, get raw numeric codes
    Age = case_when(
      Age_code == -9 ~ NA_real_,
      TRUE ~ 2024 - (2000 + (21 - Age_code))  # compute actual age
    ))

@@

@@

scores <- list(
  sample1a = add_empirical(data1a, "Sample 1a"),
  sample1b = add_empirical(data1b, "Sample 1b"),
  sample2 = add_empirical(data2, "Sample 2"),
  sample3 = add_empirical(data3, "Sample 3"),
  sample4 = add_empirical(data4, "Sample 4"),
  sample5 = add_empirical(data5, "Sample 5"),
  sample6 = add_empirical(data6, "Sample 6"),
  sample7a = add_empirical(data7a, "Sample 7a"),
  sample7b = add_empirical(data7b, "Sample 7b"),
  sample7c = add_empirical(data7c, "Sample 7c"),
  sample8a = add_empirical(data8a, "Sample 8a"),
  sample8b = add_empirical(data8b, "Sample 8b"),
  sample9 = add_empirical(data9, "Sample 9"),
  sample10 = add_empirical(data10, "Sample 10"),
  sample11 = add_empirical(data11 , "Sample 11"),
  sample12 = add_empirical(data12 , "Sample 12"),
  sample13 = add_empirical(data13, "Sample 13"),
  sample14 = add_empirical(data14 , "Sample 14"),
  sample15 = add_empirical(data15 , "Sample 15"),
  sample16 = add_empirical(data16, "Sample 16"),
  sample17 = add_empirical(data17, "Sample 16")
)

>>>>

df17 <- haven::read_sav("../data/Petzke2024/ETUDE1_main study.sav") |>
  mutate_all(as.numeric) |>
  select(age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total) |>
  rename(Age= age_to_be_completed_that_year,
         Heart = IA01_01, Hungry = IA01_02, Breathing = IA01_03, Thirsty = IA01_04, Urinate = IA01_05, 
         Defecate=IA01_06, Taste = IA01_07,Vomit = IA01_08, Sneeze = IA01_09, Cough = IA01_10, 
         Temp = IA01_11, Sex_arousal = IA01_12, Wind = IA01_13, Burp = IA01_14,Muscles = IA01_15, 
         Bruise = IA01_16, Pain = IA01_17, Blood_Sugar = IA01_18, Affective_touch = IA01_19, 
         Tickle =IA01_20, Itch = IA01_21,
         TAS_DIF = DIF_total, TAS_DDF =  DDF_total, TAS_EOT = EOT_total,
         PHQ15_Sum = PHQ_15_total,
         PHQ4_Sum = PHQ_4_total,
         BPQ_BodyAwareness = BPQ_total,
          ) |>
  mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender == 3 ~ "Other"))|>
   mutate(
    Age_code = zap_labels(Age),      # remove SPSS labels, get raw numeric codes
    Age = case_when(
      Age_code == -9 ~ NA_real_,
      TRUE ~ 2024 - (2000 + (21 - Age_code))  # compute actual age
    ))

@@

- the first optimal number of factors was 11, which, although too large for practical higher-order structure description, hints at the scattered nature of the items

@@

scores <- list(
  sample1a = add_empirical(data1a, "Sample 1a"),
  sample1b = add_empirical(data1b, "Sample 1b"),
  sample2 = add_empirical(data2, "Sample 2"),
  sample3 = add_empirical(data3, "Sample 3"),
  sample4 = add_empirical(data4, "Sample 4"),
  sample5 = add_empirical(data5, "Sample 5"),
  sample6 = add_empirical(data6, "Sample 6"),
  sample7a = add_empirical(data7a, "Sample 7a"),
  sample7b = add_empirical(data7b, "Sample 7b"),
  sample7c = add_empirical(data7c, "Sample 7c"),
  sample8a = add_empirical(data8a, "Sample 8a"),
  sample8b = add_empirical(data8b, "Sample 8b"),
  sample9 = add_empirical(data9, "Sample 9"),
  sample10 = add_empirical(data10, "Sample 10"),
  sample11 = add_empirical(data11 , "Sample 11"),
  sample12 = add_empirical(data12 , "Sample 12"),
  sample13 = add_empirical(data13, "Sample 13"),
  sample14 = add_empirical(data14 , "Sample 14"),
  sample15 = add_empirical(data15 , "Sample 15"),
  sample16 = add_empirical(data16, "Sample 16"),
  sample17 = add_empirical(data17, "Sample 17")
)

### 2025-10-31 analysis/study2.qmd
minor

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10 <- cbind(data$df10, scores$sample10)
df11 <- cbind(data$df11, scores$sample11)
df12 <- cbind(data$df12, scores$sample12)
df13 <- cbind(data$df13, scores$sample13)
df14 <- cbind(data$df14, scores$sample14)
df15 <- cbind(data$df15, scores$sample15)
df16 <- cbind(data$df16, scores$sample16)

@@

alldata <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, 
                df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, 
                df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11=df11, 
                df12=df12, df14=df14, df15=df15, df16=df16)
```

>>>>

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10 <- cbind(data$df10, scores$sample10)
df11 <- cbind(data$df11, scores$sample11)
df12 <- cbind(data$df12, scores$sample12)
df13 <- cbind(data$df13, scores$sample13)
df14 <- cbind(data$df14, scores$sample14)
df15 <- cbind(data$df15, scores$sample15)
df16 <- cbind(data$df16, scores$sample16)
dff17 <- cbind(data$df17, scores$sample17)

@@

alldata <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, 
                df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, 
                df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11=df11, 
                df12=df12, df14=df14, df15=df15, df16=df16, df17 = df17)
```
